---
title: "Simple Linear Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple Linear Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SimpLin)
```

# Introduction

This is a simple example of a simple linear regression analysis using the `SimpLin` package.
I have included one example here. You have to provide the response variable and the predictor variable to the `SimpLinR` function in that order.

```{r}
set.seed(600)
init_X <- rnorm(100)
init_Y <- 1 - init_X + rnorm(100)
r <- SimpLinR(init_Y, init_X)
```

It will produce a list of results. You can access -

1) the coefficients of the model 

```{r}
r$coefficients
    
```

2) the residuals

```{r}  
r$residuals

```
3) the fitted values

```{r}
r$fitted.values

```
4) the confidence intervals for the coefficients

```{r}
r$confidence_intervals
```

5) the standard errors of the coefficients

```{r}
r$standard_errors

```




